---
title: "Untitled"
output: html_document
---




### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r}
x<-seq(1:50)
for (i in 1:50){
  print(i)
}

```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r}
A<-seq(from=0, to=1000, by=1)
sumA<-0
for (i in A){
  sumA<-sumA + i
}
sumA
```


B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r}
B<-seq(from=0, to=1000, by=2)
sumB<-0
for (i in B){
  sumB<-sumB + i
}
sumB
```

C. Now, repeat A and B WITHOUT using a loop.
```{r}
sum(seq(from=0, to=1000))
sum(seq(from=0, to=1000, by=2))

```

### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, eval=TRUE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r}
survey.clean<-survey
for (i in 1:6){
  new<-survey.clean[,i] 
  new[new<1|new>5]<-NA 
  survey.clean[,i]<-new 
}
survey.clean

```

B. Now, again using a loop, add a new column to the dataframe called “invalid.answers” that indicates, for each participant, how many bad answers they gave.
```{r}
for (i in 1:6){
  n<-survey.clean[i,1:6] 
  survey.clean$invalid.answers[i]=sum(is.na(n))
}
survey.clean

```